Response to the defense feedback

### 2021-06-10 Chapter-6/Chapter-6.tex
update
Updates from Overleaf

\subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has a few side-channel leakages, but given the end of life status of DES, it is still unpatched for the worth of engineering effort. \detect{} also detects several leakages in asymmetric ciphers such as RSA. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which may partially explain why developers are not interested in fix all the side-channel leakages.

@@

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I apply a black box fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Population) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Sample). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data sets in
machine learning are i.i.d. i.i.d. is the foundation of many machine learning
techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
simplify many methods by assuming the data won't change over the time. 
In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
We believe the i.i.d. assumption holds under the circumstance, although the
assumption can be violated in some real-world scenarios.

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} can not cover all the paths and may miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs. For other libraries such as graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find every side-channel vulnerabilities. The goal of \ctool{} is to pick up really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.

>>>>

\subsection*{Leakages} While recent works have reported lots of potential side-channel vulnerabilities, most of them are not patched by developers. The DES implementation of OpenSSL has a few side-channel leakages, but given the end of life status of DES, it is still unpatched for the worth of engineering effort. \detect{} also detects several leakages in asymmetric ciphers such as RSA. After we manually analyze these leakage sites, we find many of them leak very little or useless information (e.g., the length of big numbers), which may partially explain why developers are not interested in fixing all the side-channel leakages.

@@

\ctool{} requires the random input variables to be independent and identically distributed (i.i.d.). That's why I apply a black box fuzzing instead of a coverage-guided fuzzing. As long as each time we get a random input from the whole input space (Population) that is independent of the previous input, the input variables should satisfy the i.i.d. assumption. For AES-128 encryption, each time we randomly generate a 128 bit key from $0$ to $2^{128}$, the sequence of key values follows the i.i.d. assumption. The situation is a little different for machine learning libraries. In the dissertation, we evaluated \ctool{} on a deep learning model. Each time, we randomly select an item from a dataset (Sample). If the dataset is biased, then we cannot get correct results. The good news is that the most well-known data sets in
machine learning are i.i.d. i.i.d. is the foundation of many machine learning
techniques (e.g., cross-validation, SVM, back-propagation). The assumption of i.i.d. 
simplify many methods by assuming the data won't change over the time. 
In my dissertation, we used MINIST, a well-known handwriting digit dataset. 
We believe the i.i.d. assumption holds under the circumstance, although the
assumption can be violated in some real-world scenarios.

\ctool{} is a dynamic approach. So it bears the same limitations of dynamic approaches as well. \ctool{} cannot cover all the paths and may miss some side-channel vulnerabilities. It is usually not a crucial problem for cryptography libraries as cryptography libraries are designed to have the same control flow under various inputs. For other libraries such as graphic rendering, machine learning, \ctool{} is very likely to miss some side-channel vulnerabilities. However, \ctool{} is not designed to find every side-channel vulnerabilities. The goal of \ctool{} is to pick up really serious side-channel vulnerabilities from the numerous vulnerabilities. So we do not think it is the main limitation of \ctool{}. However, users of \ctool{} should be aware of the code coverage problem.
